---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
data <- read.csv("superbowl.csv")
data



data$Winner.Team.Id <- as.factor(data$Winner.Team.Id)
data$Loser.Team.Id <- as.factor(data$Loser.Team.Id)

```

```{r}
g<- ggplot(data = data, aes(MVP))+
  stat_count(show.legend = TRUE, aes(color =Winner.Pts, fill = State)) +
  labs(title = "Superbowl Wins MVP vs. WINS ",
       subtitle = "1967 to 2020's ",
       x = "MVP",
       y = "Wins") +
  theme(panel.background = element_blank())

g + theme(axis.text.x = element_text(angle = 90))
  
```

#Kansas City Chiefs have both won more and participated in more total Super Bowls #than the Tampa Bay Buccaneers. but the buccaneers have a chance if they can read the #chiefs mvp

```{r}
ggplot(data = data, aes(Stadium)) + 
  stat_count(show.legend = TRUE, aes(color = Loser.Pts, fill = Loser.Team.Id)) +
  labs(title = "Superbowl Losses based on location",
       subtitle = "1967 - 2020",
       x = "Stadium",
       y = "Losses",
       caption = "Source: Kaggle") +
  coord_flip() +
  theme(panel.background = element_blank())

  
```
#based on the location the most losses occur in the rose bowl, orange bow, and #louisiana super dome. from that i can see that florida as a state usually sees more #wins than kansas overall.




```{r}
bp <- ggplot(data, aes(x="", y=Winner.Pts, fill=State)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0)

print(bp + ggtitle("Superbowl Winners Points 1967 - 2020")+ xlab("States") + ylab("Winners.pts"))
```
#I believe Florida will win the because of the overall experience they have over the #buccaneers. we can expect a good match and honestly its anyones game.

#But if i had to say i would like to say the buccaneers overall will win the super #bowl





